Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-05-19 Manuscript/proto-manuscript.tex
Some updates

%\documentclass[aip,jcp,twocolumn]{revtex4}
\documentclass[aip,jcp]{revtex4}
%\documentclass{article}

@@

% Here I write pseudo-article statements that will make the main argument.
% Beautiful polished sentences will be formed only afte we agree on these basic things
\textbf{General Introduction}

@@

\textbf{Specific introduction: current FFs and MDEC/ECC}

@@

MDEC -- or -- ECC 
\todoii{choose one}{We have to decide whether we will refer to the method as a correction (ECC) or as a MD simulation paradigm (MDEC) -- and choose on of these labels. -- Joe: use ECC as we apply MDEC rather as a correction to current state not as a new paradigm for FF development.}
MD in electronic continuum as in \cite{Leontyev2015} or electronic continuum correction as in \cite{Jungwirth2015}

@@

\textbf{Main body starts:}

@@

\textbf{Observations, how does the system behave, what are its macroscopic properties:}

@@

Gives correct scattering form factor -- reliable structural properties (especially in combination with OPs) and good ground for interpretting experimental data.

@@

Preserves other relevant properties: APL, Order Parameters (OPs of headgroup and tails), 
diffusion? \todoi{diffusion can be even improved -- and doesn't have to. We may as well omit it.}, 
elasticity? \todoi{check elastic properties -- do they change, improve, worsen?? -- likely not crucial for the main message of the paper.} 
-- however, it is still garbage in-garbage out

The glycerol backbone and headgroup order parameters are plotted in
Fig \ref{HGopsNEWmodels.eps} for reference models and EEC models. The difference,
i.e. the effect of scaling on these parameters, is shown in Fig. \ref{HGopsNEWmodelsCHANGE}.

\begin{table}
  \caption{Area per lipid from different models for POPC without ions\label{apls} }
  \begin{tabular}{c c c}
    model          & A (Å$^2$)   & Temperature [K] \\
    \hline
    Lipid14 (literature)  & 65.6$\pm$ 0.5  &  303 \\
    Lipid14ecc0.80+sigma0.875 &        &  313    \\
    GMX small patch           & 64.9   &         \\
    GMX 4xbig patch           & 65.5   &         \\
    oMM small patch           & 63.65  &         \\
    oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment \cite{Jambeck2012}\todoii{REF}{put original references, not Slipids param. paper.}  & 62.7  &  293    \\
    experiment  & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{fig:form-f}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{HGopsNEWmodels}
    Headgroup and glycerol backbone order parameters from standard Lipid14 and EECLipid17 models.}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2_surf.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of concentration of cations or cationic surfactant DHMDMAB. }
\end{figure}

>>>>

\documentclass[aip,jcp,twocolumn]{revtex4}
%\documentclass[aip,jcp]{revtex4}
%\documentclass{article}

@@

% Here I write pseudo-article statements that will make the main argument.
% Beautiful polished sentences will be formed only afte we agree on these basic things
\section{Introduction}

@@

%\textbf{Specific introduction: current FFs and MDEC/ECC}

@@

MDEC -- or -- ECC 
\todo{choose one}{We have to decide whether we will refer to the method as a correction (ECC) or as a MD simulation paradigm (MDEC) -- and choose on of these labels. -- Joe: use ECC as we apply MDEC rather as a correction to current state not as a new paradigm for FF development.}
MD in electronic continuum as in \cite{Leontyev2015} or electronic continuum correction as in \cite{Jungwirth2015}

@@

\section{Methods}

@@

\section{Results and Discussion}

Detailed and robust structural information of lipid bilayers can
be reached with C-H bond order parameter from NMR and form factors from scattering
experiments. The formed can be used to validate structures sampled by individual
molecules and latter to validate overall bilayer properties, lateral density
(area per molecule) and thickness \cite{ollila16}. The structural quality of
new ECC lipid model against scattering form factors and NMR order parameters
is evaluated in Fig. \ref{simVSexpNOions}
\todo{Add acyl chain order parameters, POPC chemical structure and fix experimental alpha order parameter value}
\todo{Why original Lipid14 models seems to deviate from experiments, in contrast to the original publication?}
\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
%  \caption{\label{fig:form-f}
%    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
%\end{figure}
%
%\begin{figure}[]
%  \centering
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and EECLipid17 models
    compared with experimental order parameters from \cite{ferreira13}.}
\end{figure}
Area per molecules extracted from MD simulations and SPD model fitted to scattering data \todo{check that this the case for the used values}
are shown in Table \ref{apls}
\todo{finalize figure and the discussion}
\begin{table}
  \caption{Area per lipid from different models for POPC without ions\label{apls} }
  \begin{tabular}{c c c}
    model          & A (Å$^2$)   & Temperature [K] \\
    \hline
    Lipid14 (literature)  & 65.6$\pm$ 0.5  &  303 \\
    Lipid14ecc0.80+sigma0.875 &        &  313    \\
    GMX small patch           & 64.9   &         \\
    GMX 4xbig patch           & 65.5   &         \\
    oMM small patch           & 63.65  &         \\
    oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment \cite{Jambeck2012}\todoii{REF}{put original references, not Slipids param. paper.}  & 62.7  &  293    \\
    experiment  & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}

Preserves other relevant properties: APL, Order Parameters (OPs of headgroup and tails), 
diffusion? \todoi{diffusion can be even improved -- and doesn't have to. We may as well omit it.}, 
elasticity? \todoi{check elastic properties -- do they change, improve, worsen?? -- likely not crucial for the main message of the paper.} 
-- however, it is still garbage in-garbage out
The glycerol backbone and headgroup order parameters are plotted in
Fig \ref{HGopsNEWmodels.eps} for reference models and EEC models. The difference,
i.e. the effect of scaling on these parameters, is shown in Fig. \ref{HGopsNEWmodelsCHANGE}.

@@

@@

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OrdParChanges_NaCl_CaCl2_surf.eps}
  \caption{\label{OrderParameterCHANGESnewMODELS}
    Headgroup order parameter changes as a function of concentration of cations or cationic surfactant DHMDMAB. }
\end{figure*}
